Data Specialization for a Staged Lambda Calculus

### 2015-06-30 paper/splitting.tex
working on splitting

First pass evaluation reduces $p$ to $b$,
which is plugged in for $l$ to produce $[b/l]r$.
Correctness of splitting states that this should be equivalent 
to the residual that would have been produced by direct evaluation.
That is, $[b/l]r \equiv q$.

Since execution of the first pass serves to generate input for
the second pass, we say $p$ is a {\em precomputation} that produces a
{\em boundary value} ($b$) for the {\em resumer} ($l.r$).

% The process of splitting \bbtwo\ terms is given by via the new
% relation~$\splittwosym$.

%masking yields the masked value $\mval i q$ (via~$\vsplito$)

>>>>

First pass evaluation reduces $p$ to $b$,
which is plugged in for $l$ to produce $[b/l]r$.
Correctness of splitting states that this should be equivalent 
to the residual produced by direct evaluation, $q$.
Since execution of the first pass serves to generate input for
the second pass, we say $p$ is a {\em precomputation} that produces a
{\em boundary value} ($b$) for the {\em resumer} ($l.r$).
More precisely, we can state correctness as \ref{thm:allCorrect}:
\begin{theorem}
\label{thm:allCorrect}
If $e \stepsym \bbtwo \cdots \stepsym \bbtwo \exv q$ and $\splitone e A p {l.r}$,
then $\reduce p b$ and $[b/l]r \equiv q$.
\end{theorem}
where $\reduce e v$ indicates standard monostage reduction of the term $e$ to the value $v$,
and $e_1 \equiv e_2$ indicates a monostage equivalence (defined later).

We prove \ref{thm:allCorrect} by induction on the steps of evaluation.  
In the base case, where $e$ is already a residual of the form $\exv q$, we know
$\splitone {\exv q} A {\exv{\tup{}}} {\_.q}$, and so by uniqueness of splitting, 
$p = b = \tup{}$ and $r = q$.
It directly follows that $\reduce {\exv {\tup {}}} {\tup {}}$ and $q \equiv q$.
